A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-07 paper/paper.Rnw
Update

\mt{For each image in the test set, the ``true labels" are nine human-assigned labels of 0 or 1 corresponding to each of the nine shape categories. When the CNN predicts which shapes are in the image, however, it assigns a probability between 0 and 1 for each shape category, with a total of nine probabilities per test image. Thus, to determine the accuracy of the model predictions, one must choose a threshold to the probabilities, such that a predicted probability above the threshold indicates a ``yes" prediction from the model and a probability below the threshold indicates a ``no". If the threshold is high, \fix{moderate} probabilities will be treated as a ``no", which increases the number of true negative and false negative predictions. Conversely, if the threshold is too low, \fix{moderate} probabilites will be considered as ``yes", which increases the true and false positive predictions in the data. An appropriate threshold must be chosen to produce a high true positive rate while also ideally keeping the false positive rate low.}

>>>>

\mt{For each image in the test set, the ``true labels" are nine human-assigned labels of 0 or 1 corresponding to each of the nine shape categories. When the CNN predicts which shapes are in the image, however, it assigns a probability between 0 and 1 for each shape category, with a total of nine probabilities per test image. Thus, to determine the accuracy of the model predictions, one must choose a threshold to the probabilities, such that a predicted probability above the threshold indicates a ``yes" prediction from the model and a probability below the threshold indicates a ``no". If the threshold is too high, \fix{moderate} probabilities will be treated as a ``no", which increases the number of true negative and false negative predictions. Conversely, if the threshold is too low, \fix{moderate} probabilites will be considered as ``yes", which increases the true and false positive predictions in the data. An appropriate threshold must be chosen to produce a high true positive rate while also ideally keeping the false positive rate low.}
